Approximation as Differentiation notes

### 2025-04-02 notes/sec/cmon-enriched.tex
Just need to fix direction of morphisms in C^op.

\noindent Now suppose $C$ is $\mathscr{V}$-enriched with $\mathscr{V}$ closed monoidal. Then the hom-functor
$\Hom{C}{-}{X}: C^\op \to \mathscr{V}$ is $\mathscr{V}$-enriched; the following diagram commutes by the
associativity of composition:

>>>>

\noindent Now suppose $C$ is $\mathscr{V}$-enriched with $\mathscr{V}$ closed monoidal; then the hom-functor
$\Hom{C}{-}{X}: C^\op \to \mathscr{V}$ is $\mathscr{V}$-enriched. The following diagram commutes because
precomposition with the identity is the identity on morphisms:

\begin{center}
\begin{tikzcd}[column sep=1.8cm]
I \arrow[d, equals] \arrow[r, "\id_X"] & \Hom{C}{X}{X} \arrow[d, "\Hom{C}{-}{W}_{X,X}"] \\
I \arrow[r, "\id_{\Hom{C}{X}{W}}"'] & \Hom{\mathscr{V}}{\Hom{C}{X}{W}}{\Hom{C}{X}{W}}
\end{tikzcd}
\end{center}

\noindent and the following by the associativity of composition:
